Online appendix for "Pandemic Pass? Treaty Derogations and Human Rights Practices During COVID-19

### 2024-07-13 manuscript/appendix.qmd
Specify column
https://github.com/vincentarelbundock/tinytable/issues/306

who_regions %>% 
  tt(width = 1) %>% 
  format_tt(escape = TRUE) %>% 
  style_tt(i = seq(1, nrow(who_regions), by = 2), bold = TRUE, background = "#e6e6e6") %>% 
  style_tt(i = seq(2, nrow(who_regions), by = 2), indent = 2, align = "l") %>% 
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}"
  )
```

>>>>

who_regions %>% 
  tt(width = 1) %>% 
  format_tt(j = 1, escape = TRUE) %>% 
  style_tt(i = seq(1, nrow(who_regions), by = 2), bold = TRUE, background = "#e6e6e6") %>% 
  style_tt(i = seq(2, nrow(who_regions), by = 2), indent = 2, align = "l") %>% 
  style_tt(
    bootstrap_class = "table table-sm",
    tabularray_inner = "rowsep=1pt, cells={font=\\footnotesize}"
  )
```
